The Impact of Educational Expenses of New Coders

### 2021-04-21 outputs/paper/paper.Rmd
Edit model evaluation tables

# summary(multiReg3)
stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
          title = "Predictions of money for learning", 
          header = FALSE,
          type = "latex")
```

@@

stargazer::stargazer(linReg1, linReg2, linReg3, linReg4,
          title = "Predictions of money for learning by city population", 
          header = FALSE,
          type = "latex",
          column.labels = c("Any", "Small", "Medium", "Large"),
          font.size = "tiny")

>>>>

# summary(multiReg3)
stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
          title = "Predictions of money for learning", 
          header = FALSE,
          type = "latex",
          column.labels = c("Model (1)", "Model (2)", "Model (3)"),
          model.numbers = FALSE)
```

@@

stargazer::stargazer(linReg1, linReg2, linReg3, linReg4,
          title = "Predictions of money for learning by city population", 
          header = FALSE,
          type = "latex",
          column.labels = c("Model (4): Any", "Model (5): Small", "Model (6): Medium", "Model (7): Large"),
          model.numbers = FALSE,
          font.size = "tiny")
